String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-08 2023-1-19/sections/introduction.tex
intro

\paragraph*{Organization} \zhilin{to be cleaned} The rest of the paper is structured as follows: Section \ref{sec:pre} introduces the preliminaries. Section \ref{sec:overview} outlines the overall algorithm. Section \ref{sec:automaton} illustrates how to construct an automaton from a regular expression. Section \ref{sec:algorithm} shows how to solve a string constraint with repetition. Section \ref{sec:implementation} presents the experimental results. Section \ref{sec:conclu} concludes the paper and discusses future work.

>>>>

\paragraph*{Organization} The rest of this paper is structured as follows: Section~\ref{sec:overview} gives an overview of the approach in this paper. Section~\ref{sec:pre} introduces the preliminaries. 
Section~\ref{sec:recl} presents the syntax and semantics of RECL. 
Section~\ref{sec:automaton} defines CEFA. Section~\ref{sec:algorithm} introduces the algorithm to solve RECL constraints. Section~\ref{sec:implementation} shows the experiment results. Section~\ref{sec:conclu} concludes this paper.
